Test parsing of Proff.no table (Kreftforeningen)

### 2022-07-07 Test parsing of Proff table.Rmd
Fixed missing intermediate df. Style fixes.
Testing with different organisation. Unfortunately errors. Creating function.

@@

# Viewing table
table_kreft8 |>
  arrange(desc(year))

# Quick visualisation
table_kreft8 |> 
  filter(year == 2021) |> 
  ggplot(aes(REGNSKAPSPERIODE, value)) +
  geom_col() +
  coord_flip()
```

@@

```{r}

>>>>

table_kreft2 <- table_kreft

@@

# Quick visualisation
table_kreft8 |> 
  filter(year == 2021) |> 
  ggplot(aes(REGNSKAPSPERIODE, value)) +
  geom_col() +
  coord_flip()

# Removing values that are years
table_kreft9 <- table_kreft8 |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )

# Viewing table
table_kreft9 |>
  arrange(desc(year))
```

@@

```{r opera}
# Reading saved html
opera <- read_html("Links/opera.html") |> 
  html_node("#inner-frame") |> 
  html_table()

opera2 <- opera

# Removing white space
opera2$REGNSKAPSPERIODE <- opera2$REGNSKAPSPERIODE |>
  str_squish()

# Removing empty column
opera3 <- opera2 |>
  select(REGNSKAPSPERIODE:`2002`)

# Removing duplicate rows
opera4 <- opera3 |>
  filter(!grepl("Lukk", REGNSKAPSPERIODE))

opera5 <- opera4 |>
  pivot_longer(`2021`:`2002`, names_to = "year")

opera6 <- opera5

# Turning "-" into NA
opera6 <- opera6 |> 
  mutate(value = na_if(value, "-"))

# Turning years into integers
opera6$year <-as.integer(opera6$year)

# Removing unnecessary dates
opera7 <- opera6 |> 
  filter(
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode")

# Removing whitespace
opera8 <- opera7 |> 
  mutate(
    value = str_replace_all(value, "\\s", "")
  )

# Converting to numbers
opera8 <- opera8 |> 
  mutate(
    value = as.numeric(value)
  )

# Removing values that are years
opera9 <- opera8 |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )

# Viewing table
opera9 |>
  arrange(desc(year))

opera9 |> 
  mutate(
    error = year - value
  ) |> 
  filter(error == 1)

# Result: duplicated entries with wrong year
```

```{r single operation}
opera_test <- read_html("Links/opera.html") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select(
    REGNSKAPSPERIODE:`2002`) |> 
  mutate(
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
  filter(
    !grepl("Lukk", REGNSKAPSPERIODE)) |> 
  pivot_longer(
    `2021`:`2002`, names_to = "year") |> 
  mutate(
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  filter(
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate(
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate(
    value = as.numeric(value)
  ) |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )

read_proff <- function(file){
  read_html(file) |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select(
    REGNSKAPSPERIODE:`2002`) |> 
  mutate(
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
  filter(
    !grepl("Lukk", REGNSKAPSPERIODE)) |> 
  pivot_longer(
    `2021`:`2002`, names_to = "year") |> 
  mutate(
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  filter(
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate(
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate(
    value = as.numeric(value)
  ) |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )
}

read_proff("Links/opera.html")
